### 2016-08-19 introduction.tex
Clarify reviewer 3 point 1 a bit more

Python is a dynamically typed programming language that has a focus on
ease of use and readability. Due in part to this focus, it has become a popular
language for scientific
computing and data science, with a broad ecosystem of
libraries~\cite{oliphant2007python}. SymPy is itself used by many libraries
and tools to support research within a variety of domains, such as
SageMath~\cite{sagemath} (pure and applied mathematics),
yt~\cite{2011ApJS..192....9T} (astronomy and astrophysics),
PyDy~\cite{gede2013constrained} (multibody dynamics), and
SfePy~\cite{cimrman2014sfepy} (finite elements).

@@

The following statement imports all SymPy functions into the global Python
namespace.\footnote{\texttt{import *} has been used here to aid the
  readability of the paper, but is best to avoid such wildcard import
  statements in production code, as they make it unclear which names are
  present in the namespace. Furthermore, imported names could clash with
  already existing imports from another package. For example, SymPy, the
  standard Python \texttt{math} library, and NumPy all define the \texttt{exp}
  function, but only the SymPy one will work with SymPy symbolic expressions.}
From here on, all examples in this paper assume that this statement has been
executed:\footnote{Three greater-than signs denote standard
Python prompt for interactive session.}

>>>>

Python is a dynamically typed programming language that has a focus on
ease of use and readability.\footnote{This paper assumes a moderate
  familiarity with the Python programming language.} Due in part to this focus, it has become a popular
language for scientific
computing and data science, with a broad ecosystem of
libraries~\cite{oliphant2007python}. SymPy is itself used by many libraries
and tools to support research within a variety of domains, such as
SageMath~\cite{sagemath} (pure and applied mathematics),
yt~\cite{2011ApJS..192....9T} (astronomy and astrophysics),
PyDy~\cite{gede2013constrained} (multibody dynamics), and
SfePy~\cite{cimrman2014sfepy} (finite elements).

@@

The following statement imports all SymPy functions into the global Python
namespace.\footnote{\texttt{import *} has been used here to aid the
  readability of the paper, but is best to avoid such wildcard import
  statements in production code, as they make it unclear which names are
  present in the namespace. Furthermore, imported names could clash with
  already existing imports from another package. For example, SymPy, the
  standard Python \texttt{math} library, and NumPy all define the \texttt{exp}
  function, but only the SymPy one will work with SymPy symbolic expressions.}
From here on, all examples in this paper assume that this statement has been
executed:\footnote{The three greater-than signs denote the user input for the
  Python interactive session, with the result, if there is one, shown on the
  next line.}
